A continental-scale analysis finds generalists, with large clutch size and residual brain mass, are the most urban-tolerant of birds

### 2018-06-03 ms.Rmd
some work on phylo sig table

library(kableExtra)
library(pander)
pander(table, caption = "Results showing the significance of the phylogenetic signal analyses, for a suite of indices.", split.table=Inf)

>>>>

library(kableExtra)
library(pander)
pander(table, caption = "Results showing the  phylogenetic signal for both predictor and response traits.  Because there are a number of indices in the literature, with specific strengths and weaknesses, we present here all available indices (Keck et al. 2016).", split.table=Inf)
